Lens Modeling in \sw

### 2013-09-09 text/tex/intro.tex
commit to be merged

Spacewarps is the future.\needcite

Moreover, that lens modelling is an essential accompaniment to lens
searches has been clear since the early days \citep{1981ApJ...244..723Y}.

Why Fermat's principle?  Details in \ref{sec:Fermat} and
\ref{sec:more-theory}.

SpaghettiLens details in \ref{sec:SpaghettiLens}.

Sims in \ref{sec:sims}.

\needfig[testfig]

Results in \ref{sec:results}.

Things to do in \ref{sec:todo}.

This is a general test \secref{todo}\todo{remove this part again}

\hr

Gravitational Lensing, prediced bz ART and first confirmed by ... can be used as a tool by astronomers to examine structres far away.
Allows to esimate masses, not only visual but total masses (inkl dark matter).
Further more, allows to esimate cosmologial parameters, like Hubblekonst (Age of universe \needcite) and massdenity \needcite.
To accheve this, one needs to find / identify lenses and in a second step model those lenses to get involved parameters.

@@

Next step involves modelling. that needs advanced knolegde and takes a lot of time.
Too much time to be done by astronomers them selves as the results from new surveys and identifiers like \sw come in.
So there is a demand of a means to modell a great amount of identified lens data, that scales with increasing data amount.

>>>>

%Spacewarps is the future.\needcite
%
%Moreover, that lens modelling is an essential accompaniment to lens
%searches has been clear since the early days \citep{1981ApJ...244..723Y}.
%
%Why Fermat's principle?  Details in \ref{sec:Fermat} and
%\ref{sec:more-theory}.
%
%SpaghettiLens details in \ref{sec:SpaghettiLens}.
%
%Sims in \ref{sec:sims}.
%
%\needfig[testfig]
%
%Results in \ref{sec:results}.
%
%Things to do in \ref{sec:todo}.
%
%This is a general test \secref{todo}\todo{remove this part again}
%
%\hr

Gravitational lenses (GLs), predicted by ART, can be used as a tool by astronomers to examine many properties of the cosmos.
They allow for example to estimate the masses and their distribution of galaxies, automatically including the hard to grasp dark matter.
Further more, they allow an estimate on cosmological parameters like the Hubble constant \citep{Saha2006} and the mass density \needcite.

%To accheve this, one needs to find / identify lenses and in a second step model those lenses to get involved parameters.

@@

Next step involves modeling. that needs advanced knolegde and takes a lot of time.
Too much time to be done by astronomers them selves as the results from new surveys and identifiers like \sw come in.
So there is a demand of a means to modell a great amount of identified lens data, that scales with increasing data amount.
